Sparse spectral methods for partial differential equations on spherical caps

### 2020-11-06 papers/spherical-caps/spherical-caps.tex
Addressed comments.

@@

Note that we consider partial differential operators that are not necessarily rotational invariant:  for example, one can use these techniques for  Schr\"odinger operators $\DeltaS + V(x,y,z)$ where $V$ is first approximated by a polynomial. A nice feature though is that if the partial differential operator is invariant with respect to rotation around the $z$ axes (e.g., a Schr\"odinger operator with potential $V(z)$) the discretisation decouples, and can be reordered as a block-diagonal matrix. This improves the complexity further to an optimal $O(p^2$), which is demonstrated\sotodo{This isn't actually shown in the referenced figure, which shows a non-radially symmetric potential Also, we need to make $V$ vs $v$ consistent with the figures and example} in Figure \ref{fig:complexity} with $V(x,y,z) = \cos z$.

@@

\begin{proposition}[\cite{olver2020orthogonal}]\label{prop:construction}
	Let $w : (\alpha,\beta) \: \to \R$ be a weight function. For $n = 0,1,2,\dots, $ let $\{r_{n,k}\}$ be polynomials orthogonal with respect to the weight $\rho(x)^{2k} w(x)$ where $0 \le k \le n$. Then the 3D polynomials defined on $\Omega$\sotodo{Make notation consistent with Def 3, i.e., whether you use $\xvec$ or not}
\begin{align*}
	\scopnki(x,y,z) \equiv \scopnki(\xvec,z) := r_{n-k,k}(z) \: \rho(z)^k \: \ch_{k,i}\fpr(\frac{\xvec}{\rho(z)})
\end{align*}
for $i \in {0,1}, \: 0 \le k \le n, \: n = 0,1,2,\dots$ are orthogonal polynomials with respect to the inner product
\begin{align*}
	\ip< p, \: q > &:= \int_\Omega p(x,y,z) \: q(x,y,z) \: w(z) \: \D A \\
	&= \int_0^{\cos^{-1}(\alpha)} \int_0^{2\pi} p\big(\sinphi \costheta, \sinphi \sintheta, \cosphi \big) \: q\big(\sinphi \costheta, \sinphi \sintheta, \cosphi \big) \: w(\cosphi) \: \sinphi \: \D \theta \: \D \varphi \\
	&= \int_\alpha^1 \int_0^{2\pi} p\big(\rho(z) \cos\theta, \rho(z) \sin\theta, z\big) \: q\big(\rho(z) \cos\theta, \rho(z) \sin \theta, z\big) \: w(z) \: \D \theta \: \D z
\end{align*}
on $\Omega$, where $\D A = \sinphi \: \D \theta \: \D \varphi$ is the uniform spherical measure on $\Omega$. 
\end{proposition}

@@

By construction, $\{\scopnkia\}$ are orthogonal with respect to the inner product
\begin{align*}
	\ip< p, \: q >_{\scopa} &:= \int_\Omega p(\xvec, z) \: q(\xvec, z) \: \genjacw^{(a,0)}(z) \: \D \sigma(\xvec, z) \\
	&= \int_\alpha^1 \int_0^{2\pi} p(\rho(z) \cos\theta, \rho(z) \sin\theta, z) \: q(\rho(z) \cos\theta, \rho(z) \sin\theta, z) \: \D \theta \: \genjacw^{(a,0)}(z) \: \D z,
\end{align*}
with
\begin{align}
	\norm{\scopnkia}_{\scopa}^2 &:= \ip< \scopnkia, \: \scopnkia >_{\scopa} = \pi \: \normgenjac^{(a, 2k)}. \label{eqn:normscop}
\end{align}
We note that the weight $\genjacw^{(a,b)}(z)$ has been used in the construction of 2D orthogonal polynomials on disk-slices and trapeziums \cite{snowball2019sparse}, where a method for obtaining recurrence coefficients and evaluating integrals was established (the weight is in fact semi-classical, and is equivalent to a generalized Jacobi weight \cite[\S5]{magnus1995painleve}).

@@

	&= \int_\Omega \scopnkia(\xvec,z) \: \scopmjha(\xvec,z) \: x \: \genjacw^{(a,0)}(z) \: \D\sigma(\xvec, z) \\

@@

	&= \int_\Omega \scopnkia(\xvec,z) \: \scopmjha(\xvec,z) \: y \: \genjacw^{(a,0)}(z) \: \D\sigma(\xvec, z) \\

@@

The recurrences in Lemma \ref{lemma:Qrecurrence} lead to Jacobi operators that correspond to multiplication by $x$, $y$ and $z$. Let $N \in \N$ and define notation that groups degree $N$ polynomials together: 
\begin{align}
	\bigscopNka &:= 
		\begin{pmatrix}
			\scopa_{k,k,0}(x,y,z) \\
			\scopa_{k,k,1}(x,y,z) \\
			\vdots \\
			\scopa_{N,k,0}(x,y,z) \\
			\scopa_{N,k,1}(x,y,z)
		\end{pmatrix} \in \R^{2(N-k+1)},  \quad k = 1,\dots,N, \label{eqn:OPdefNka} \\ 
	\bigscopa_{N,0} &:= 
		\begin{pmatrix}
			\scopa_{0,0,0}(x,y,z) \\
			\vdots \\
			\scopa_{N,0,0}(x,y,z) \\
		\end{pmatrix} \in \R^{N+1}, \label{eqn:OPdefN0a} \\
	\bigscopNa &:= 
		\begin{pmatrix}
			\bigscopa_{N,0} \\
			\vdots \\
			\bigscopa_{N,N}
		\end{pmatrix} \in \R^{(N+1)^2} \label{eqn:OPdefNa}
\end{align}
and set $J_x^{(a)}, J_y^{(a)}, J_z^{(a)}$ as the Jacobi matrices corresponding to
\sotodoinline{The following is wrong as it only applies if $N = \infty$} 
\bstodoinline{What is better? To define them in this way for $N \to \infty$? Or to include the extra terms in this defn below? Or just state that the Jacobi operators approximate multiplication by x,y,z? This also relates to the next comments}
\sotodoinline{If we get rid of them as suggested below this is no longer an issue}
\begin{align}
	J_x^{(a)} \: \bigscopNa(x,y,z) = x \: \bigscopNa(x,y,z), \nonumber \\
	J_y^{(a)} \: \bigscopNa(x,y,z) = y \: \bigscopNa(x,y,z), \label{eqn:jacobimatricesdefinition} \\
	J_z^{(a)} \: \bigscopNa(x,y,z) = z \: \bigscopNa(x,y,z). \nonumber
\end{align}
The matrices $J_x^{(a)}, J_y^{(a)}, J_z^{(a)}$ act on the coefficients vector of a function's expansion in the $\{\scopnkia\}$ basis. For example, let $a$ be a general parameter and let a function $f(x,y,z)$ defined on $\Omega$ be approximated up to order $N \in \N$ by its expansion $f(x,y,z) = \bigscopNa(x,y,z)^\top \mathbf{f}$. Then $x \: f(x,y,z)$ is approximated by $\bigscopNa(x,y,z)^\top {J_x^{(a)\top}} \mathbf{f}$. In other words, ${J_x^{(a)\top}} \mathbf{f}$ is the coefficients vector for the expansion of the function $(x,y,z) \mapsto x \: f(x,y,z)$ in the  $\{\scopnkia\}$ basis. Note that $J_x^{(a)}, J_y^{(a)}, J_z^{(a)}$ are banded-block-banded matrices:

@@

For example, $J_x^{(a)}, J_y^{(a)}$ are block-tridiagonal (block-bandwidths $(1,1)$) while $J_z^{(a)}$ is block-diagonal (block-bandwidths $(0,0)$):
\begin{align*}
	J_{x/y/z}^{(a)} &= 
		\begin{pmatrix}
			B^{(a)}_{x/y/z, 0} & A^{(a)}_{x/y/z, 0} & & & & \\
			C^{(a)}_{x/y/z, 1} & B^{(a)}_{x/y/z, 1} & A^{(a)}_{x/y/z, 1} & & & \\
			& C^{(a)}_{x/y/z, 2} & B^{(a)}_{x/y/z, 2} & A^{(a)}_{x/y/z, 2} & & & \\
			& & C^{(a)}_{x/y/z, 3} & \ddots & \ddots & \\
			& & & \ddots & \ddots & \ddots \\
		\end{pmatrix}
\end{align*}

For $J_x^{(a)}$, the sub-blocks $A^{(a)}_{x, k}, C^{(a)}_{x, k}$ have sub-block-bandwidths $(4,4)$ while the sub-blocks $B^{(a)}_{x,k}$ are zero matrices:
\begin{align*}
	B^{(a)}_{x,0} &= 0 \in \R^{(N+1)\times(N+1)}, \quad B^{(a)}_{x,k} = 0 \in \R^{2(N-k+1)\times2(N-k+1)} \text{ for } k = 1,2,\dots,N \\
	A^{(a)}_{x,k} &:= 
		\begin{pmatrix}
			A^{(a)}_{k,k,6} & & & \\
			A^{(a)}_{k+1,k,4} & \ddots & & \\
			A^{(a)}_{k+2,k,2} & \ddots & \ddots & \\
			& \ddots & \ddots & A^{(a)}_{N-1,k,6} \\
			& & A^{(a)}_{N,k,2} & A^{(a)}_{N,k,4}
		\end{pmatrix}, \quad k = 0,1,2,\dots,N 
\end{align*}
so that  $A^{(a)}_{x,0} \in \R^{(N+1)\times2N}$,  $A^{(a)}_{x,k} \in \R^{2(N-k+1)\times2(N-k)}$ for $k = 1,2,\dots,N$,
\begin{align*}
	C^{(a)}_{x,k} &:= 
		\begin{pmatrix}
			A^{(a)}_{k,k,1} & A^{(a)}_{k,k,3} & A^{(a)}_{k,k,5} & & \\
			& \ddots & \ddots & \ddots \\
			& & \ddots & \ddots & A^{(a)}_{N-1,k,5} \\
			& & & A^{(a)}_{N,k,1} & A^{(a)}_{N,k,3}
		\end{pmatrix}, \quad k = 1,2,\dots,N 
\end{align*}
so that $C^{(a)}_{x,1} \in \R^{2N\times(N+1)}$,  $C^{(a)}_{x,k} \in \R^{2(N-k+1)\times2(N-k+2)}$  for  $k = 2,3,\dots,N$, here for $k = 1,\dots,N, \: n = k,\dots,N$,
\begin{align}
	A^{(a)}_{n,k,j} &:= 
		\begin{pmatrix}
			\alphaa_{n,k,j} & 0 \\
			0 & \alphaa_{n,k,j}
		\end{pmatrix} \in \R^{2\times2}, (k \ne 1 \text { for } j \text{ odd}) \label{eqn:jacobisubblocksA1} \\
	A^{(a)}_{n,0,j} &:=
		\begin{pmatrix}
			\alphaa_{n,0,j} & 0
		\end{pmatrix} \in \R^{1\times2}, j \text{ odd} \label{eqn:jacobisubblocksA2} \\
	A^{(a)}_{n,1,j} &:=
		\begin{pmatrix}
			\alphaa_{n,1,j} \\
			0
		\end{pmatrix} \in \R^{2\times1}, j \text{ odd} \label{eqn:jacobisubblocksA3} \\
\end{align}

For $J_y^{(a)}$, the sub-blocks have sub-block-bandwidths $(5,5)$ while the sub-blocks $B^{(a)}_{y,k}$ are zero matrices:
\begin{align*}
	B^{(a)}_{y,0} &= 0 \in \R^{(N+1)\times(N+1)}, \quad B^{(a)}_{y,k} = 0 \in \R^{2(N-k+1)\times2(N-k+1)} \text{ for } k = 1,2,\dots,N \\
	A^{(a)}_{y,k} &:= 
		\begin{pmatrix}
			B^{(a)}_{k,k,6} & & & \\
			B^{(a)}_{k+1,k,4} & \ddots & & \\
			B^{(a)}_{k+2,k,2} & \ddots & \ddots & \\
			& \ddots & \ddots & B^{(a)}_{N-1,k,6} \\
			& & B^{(a)}_{N,k,2} & B^{(a)}_{N,k,4}
		\end{pmatrix}, \quad k = 0,1,2,\dots,N \\
	&\big( \text{so that } A^{(a)}_{y,0} \in \R^{(N+1)\times2N}, \quad A^{(a)}_{y,k} \in \R^{2(N-k+1)\times2(N-k)} \text{ for } k = 1,2,\dots,N \big) \\
	C^{(a)}_{y,k} &:= 
		\begin{pmatrix}
			B^{(a)}_{k,k,1} & B^{(a)}_{k,k,3} & B^{(a)}_{k,k,5} & & \\
			& \ddots & \ddots & \ddots \\
			& & \ddots & \ddots & B^{(a)}_{N-1,k,5} \\
			& & & B^{(a)}_{N,k,1} & B^{(a)}_{N,k,3}
		\end{pmatrix}, \quad k = 1,2,\dots,N \\
	&\big( \text{so that } C^{(a)}_{y,1} \in \R^{2N\times(N+1)}, \quad C^{(a)}_{y,k} \in \R^{2(N-k+1)\times2(N-k+2)} \text{ for } k = 2,3,\dots,N \big)
\end{align*}
where for $k = 1,\dots,N, \: n = k,\dots,N$
\begin{align}
	B^{(a)}_{n,k,j} &:= 
		\begin{pmatrix}
			0 & \betaa_{n,k,0,j} \\
			\betaa_{n,k,1,j} & 0
		\end{pmatrix} \in \R^{2\times2}, (k \ne 1 \text { for } j \text{ odd}) \label{eqn:jacobisubblocksB1} \\
	B^{(a)}_{n,0,j} &:=
		\begin{pmatrix}
			0 & \betaa_{n,0,0,j}
		\end{pmatrix} \in \R^{1\times2}, j \text{ odd}  \label{eqn:jacobisubblocksB2} \\
	B^{(a)}_{n,1,j} &:=
		\begin{pmatrix}
			0 \\
			\betaa_{n,1,1,j}
		\end{pmatrix}\in \R^{2\times1}, j \text{ odd}  \label{eqn:jacobisubblocksB3} \\
\end{align}

For $J_z^{(a)}$, the sub-blocks $B^{(a)}_{z,k}$ have sub-block-bandwidths $(2,2)$, while the sub-blocks $A^{(a)}_{z,k}, \: C^{(a)}_{z,k}$ are zero matrices:
\begin{align*}
	A^{(a)}_{z,0} &= 0 \in \R^{(N+1)\times2N}, \quad A^{(a)}_{z,k} = 0 \in \R^{2(N-k+1)\times2(N-k)} \text{ for } k = 1,2,\dots,N \\
	C^{(a)}_{z,1} &= 0 \in \R^{2N\times(N+1)}, \quad C^{(a)}_{z,k} = 0 \in \R^{2(N-k+1)\times2(N-k+2)} \text{ for } k = 2,3,\dots,N \\
	B^{(a)}_{z,k} &:= 
		\begin{pmatrix}
			\Gamma^{(a)}_{k,k,2} & \Gamma^{(a)}_{k,k,3} & \\
			\Gamma^{(a)}_{k+1,k,1} & \ddots & \ddots & \\
			& \ddots & \ddots & \Gamma^{(a)}_{N-1,k,3} \\
			& & \Gamma^{(a)}_{N,k,1} & \Gamma^{(a)}_{N,k,2}
		\end{pmatrix}  \quad k = 0,1,2,\dots,N \\
	&\big( \text{so that } B^{(a)}_{z,0} \in \R^{(N+1)\times(N+1)}, \quad B^{(a)}_{z,k} \in \R^{2(N-k+1)\times2(N-k+1)} \text{ for } k = 1,2,\dots,N \big)
\end{align*}
where for $k = 1,\dots,N, \: n = k,\dots,N$
\begin{align}
	\Gamma^{(a)}_{n,k,j} &:= 
		\begin{pmatrix}
			\gamma_{n,k,j} & 0 \\
			0 & \gamma_{n,k,j}
		\end{pmatrix} \in \R^{2\times2}, \label{eqn:jacobisubblocksGamma1} \\
	\Gamma^{(a)}_{n,0,j} &:= \gammaa_{n,0,j}. \label{eqn:jacobisubblocksGamma2}
\end{align}

@@

In this section, we introduce new notation for a different ordering of the OP vector, in order to demonstrate how we can obtain a recurrence for the OPs in matrix-vector form, and derive the associated \textit{recurrence coefficient matrices} -- we define these as the matrices derived from the OP's $x,y,z$-multiplication relationships that form the coefficients for the multidimensional three-term recurrences.

While in Section \ref{subsection:jacobimats} the ordering used is convenient for the application of Jacobi and differential operators to the vector of coefficients of a given function's expansion, the ordering we will use in this section is convenient for building the OPs and more importantly obtaining the recurrence coefficient matrices necessary for efficient function evaluation using the Clenshaw algorithm. In practice, it is simply a matter of converting coefficients between the two orderings. To this end, we define our OP-building ordering as follows. For $n=0,1,2,\dots$:
\begin{align*}
	\bigscoptna := 
		\begin{pmatrix}
			\scopa_{n,0,0}(x,y,z) \\
			\scopa_{n,1,0}(x,y,z) \\
			\scopa_{n,1,1}(x,y,z) \\
			\vdots \\
			\scopa_{n,n,0}(x,y,z) \\
			\scopa_{n,n,1}(x,y,z)
		\end{pmatrix} \in \R^{2n+1}, 
	\quad \quad 
	\bigscopta := 
		\begin{pmatrix}
			\bigscopta_0 \\
			\bigscopta_1 \\
			\bigscopta_2 \\
			\vdots \\
		\end{pmatrix}
\end{align*}
and set $\tilde J_x^{(a)}, \tilde J_y^{(a)}, \tilde J_z^{(a)}$ as the Jacobi matrices corresponding to 
\sotodoinline{Can the following be simplified? Seems like it repeats} 
\bstodoinline{Is it worth removing the previous? And just explaining that we can reorder the Jacobi matrices according to the OP/coefficient vector ordering? This section is important for deriving how to build the OPs, whereas before I simply need to say that the Jacobi operators that apply to coefficients vectors are reorderings of the ones in this section.}
\sotodoinline{I agree: get rid of the previous definition and remove the tilde from these polynomials, as they are the "default" ones}
\begin{align}
	\tilde J_x^{(a)} \: \bigscopta(x,y,z) = x \: \bigscopta(x,y,z), \nonumber \\
	\tilde J_y^{(a)} \: \bigscopta(x,y,z) = y \: \bigscopta(x,y,z), \label{eqn:jacobimatricesdefinitionalt} \\
	\tilde J_z^{(a)} \: \bigscopta(x,y,z) = z \: \bigscopta(x,y,z). \nonumber
\end{align}
where
\begin{align*}
	\tilde J_{x/y/z}^{(a)} &= 
		\begin{pmatrix}
			\tilde B^{(a)}_{x/y/z, 0} & \tilde A^{(a)}_{x/y/z, 0} & & & & \\
			\tilde C^{(a)}_{x/y/z, 1} & \tilde B^{(a)}_{x/y/z, 1} & \tilde A^{(a)}_{x/y/z, 1} & & & \\
			& \tilde C^{(a)}_{x/y/z, 2} & \tilde B^{(a)}_{x/y/z, 2} & \tilde A^{(a)}_{x/y/z, 2} & & & \\
			& & \tilde C^{(a)}_{x/y/z, 3} & \ddots & \ddots & \\
			& & & \ddots & \ddots & \ddots \\
		\end{pmatrix}.
\end{align*}
These matrices are then block-tridiagonal (block-bandwidths $(1,1)$).

>>>>

\bstodoinline{You mentioned before that you didnt like the use of $i$ being an index thoughout (as in $n,k,i$}. Is this still the case?}

@@

Note that we consider partial differential operators that are not necessarily rotational invariant:  for example, one can use these techniques for  Schr\"odinger operators $\DeltaS + v(x,y,z)$ where $v$ is first approximated by a polynomial. A nice feature though is that if the partial differential operator is invariant with respect to rotation around the $z$ axis (e.g., a Schr\"odinger operator with potential $v(z)$) the discretisation decouples, and can be reordered as a block-diagonal matrix. This improves the complexity further to an optimal $O(p^2$), which is demonstrated in Figure \ref{fig:complexity} with $v(x,y,z) = \cos z$.
\sotodoinline{This isn't actually shown in the referenced figure, which shows a non-radially symmetric potential} 
\bstodoinline{I dont really understand - isnt $V(x,y,z) =  V(z) = \cos z$ valid? I could be wrong but are you confusing this with the helmholtz example, with a different function $v$? If so, maybe I should make this clearer.}

@@

\begin{proposition}[\cite{olver2020orthogonal}]\label{prop:construction}
	Let $w : (\alpha,\beta) \: \to \R$ be a weight function. For $n = 0,1,2,\dots, $ let $\{r_{n,k}\}$ be polynomials orthogonal with respect to the weight $\rho(x)^{2k} w(x)$ where $0 \le k \le n$. Then the 3D polynomials defined on $\Omega$
\begin{align*}
	\scopnki(x,y,z) := r_{n-k,k}(z) \: \rho(z)^k \: \ch_{k,i}\fpr({x \over \rho(z)}, {y \over \rho(z)})
\end{align*}
for $i \in {0,1}, \: 0 \le k \le n, \: n = 0,1,2,\dots$ are orthogonal polynomials with respect to the inner product
\begin{align*}
	\ip< p, \: q > &:= \int_\Omega p(x,y,z) \: q(x,y,z) \: w(z) \: \D A \\
	&= \int_0^{\cos^{-1}(\alpha)} \int_0^{2\pi} p\big(\sinphi \costheta, \sinphi \sintheta, \cosphi \big) \: q\big(\sinphi \costheta, \sinphi \sintheta, \cosphi \big) \: w(\cosphi) \: \sinphi \: \D \theta \: \D \varphi \\
	&= \int_\alpha^1 \int_0^{2\pi} p\big(\rho(z) \cos\theta, \rho(z) \sin\theta, z\big) \: q\big(\rho(z) \cos\theta, \rho(z) \sin \theta, z\big) \: w(z) \: \D \theta \: \D z
\end{align*}
on $\Omega$, where $\D A = \sinphi \: \D \theta \: \D \varphi$ is the uniform spherical measure on $\Omega$. 
\end{proposition}

@@

By construction, $\{\scopnkia\}$ are orthogonal with respect to the inner product
\begin{align*}
	\ip< p, \: q >_{\scopa} &:= \int_\Omega p(\xvec, z) \: q(\xvec, z) \: \genjacw^{(a,0)}(z) \: \D A \\
	&= \int_\alpha^1 \int_0^{2\pi} p(\rho(z) \cos\theta, \rho(z) \sin\theta, z) \: q(\rho(z) \cos\theta, \rho(z) \sin\theta, z) \: \D \theta \: \genjacw^{(a,0)}(z) \: \D z,
\end{align*}
with
\begin{align}
	\norm{\scopnkia}_{\scopa}^2 &:= \ip< \scopnkia, \: \scopnkia >_{\scopa} = \pi \: \normgenjac^{(a, 2k)}. \label{eqn:normscop}
\end{align}
We note that the weight $\genjacw^{(a,b)}(z)$ has been used in the construction of 2D orthogonal polynomials on disk-slices and trapeziums \cite{snowball2019sparse}, where a method for obtaining recurrence coefficients and evaluating integrals was established (the weight is in fact semi-classical, and is equivalent to a generalized Jacobi weight \cite[\S5]{magnus1995painleve}).

@@

	&= \int_\Omega \scopnkia(\xvec,z) \: \scopmjha(\xvec,z) \: x \: \genjacw^{(a,0)}(z) \: \D A \\

@@

	&= \int_\Omega \scopnkia(\xvec,z) \: \scopmjha(\xvec,z) \: y \: \genjacw^{(a,0)}(z) \: \D A \\

@@

The recurrences in Lemma \ref{lemma:Qrecurrence} lead to Jacobi operators that correspond to multiplication by $x$, $y$ and $z$. In later sections we will use an ordering of the OPs so that they are grouped by Fourier mode $k$, which is convenient for the application of differential and other operators to the vector of coefficients of a given function's expansion (some operators will exploit this ordering for operators where Fourier modes do not interact, and thus will be block-diagonal). Before that though, the ordering we will use in the remainder of this section is convenient for establishing Jacobi operators for multiplication by $x$, $y$ and $z$, and hence building the OPs and importantly obtaining the associated \textit{recurrence coefficient matrices} necessary for efficient function evaluation using the Clenshaw algorithm. In practice, it is simply a matter of converting coefficients between the two orderings. To this end, we define our OP-building ordering as follows. For $n=0,1,2,\dots$:
\begin{align*}
	\bigscoptna := 
		\begin{pmatrix}
			\scopa_{n,0,0}(x,y,z) \\
			\scopa_{n,1,0}(x,y,z) \\
			\scopa_{n,1,1}(x,y,z) \\
			\vdots \\
			\scopa_{n,n,0}(x,y,z) \\
			\scopa_{n,n,1}(x,y,z)
		\end{pmatrix} \in \R^{2n+1}, 
	\quad \quad 
	\bigscopta := 
		\begin{pmatrix}
			\bigscopta_0 \\
			\bigscopta_1 \\
			\bigscopta_2 \\
			\vdots \\
		\end{pmatrix}
\end{align*}
and set $\tilde J_x^{(a)}, \tilde J_y^{(a)}, \tilde J_z^{(a)}$ as the Jacobi matrices corresponding to
\begin{align}
	\tilde J_x^{(a)} \: \bigscopta(x,y,z) = x \: \bigscopta(x,y,z), \nonumber \\
	\tilde J_y^{(a)} \: \bigscopta(x,y,z) = y \: \bigscopta(x,y,z), \label{eqn:jacobimatricesdefinitionalt} \\
	\tilde J_z^{(a)} \: \bigscopta(x,y,z) = z \: \bigscopta(x,y,z). \nonumber
\end{align}
where
\begin{align*}
	\tilde J_{x/y/z}^{(a)} &= 
		\begin{pmatrix}
			\tilde B^{(a)}_{x/y/z, 0} & \tilde A^{(a)}_{x/y/z, 0} & & & & \\
			\tilde C^{(a)}_{x/y/z, 1} & \tilde B^{(a)}_{x/y/z, 1} & \tilde A^{(a)}_{x/y/z, 1} & & & \\
			& \tilde C^{(a)}_{x/y/z, 2} & \tilde B^{(a)}_{x/y/z, 2} & \tilde A^{(a)}_{x/y/z, 2} & & & \\
			& & \tilde C^{(a)}_{x/y/z, 3} & \ddots & \ddots & \\
			& & & \ddots & \ddots & \ddots \\
		\end{pmatrix}.
\end{align*}
Note that $J_x^{(a)}, J_y^{(a)}, J_z^{(a)}$ are \textit{banded-block-banded matrices}:

@@

Each of these Jacobi matrices are then block-tridiagonal (block-bandwidths $(1,1)$). For $\tilde J_x^{(a)}$, the sub-blocks have sub-block-bandwidths $(2,2)$:
\begin{align*}
	\tilde A^{(a)}_{x,n} &:= 
		\begin{pmatrix}
			0 & A^{(a)}_{n,0,6} & 0 & & \\
			A^{(a)}_{n,1,5} & \ddots & \ddots & & \\
			& \ddots & \ddots & \ddots & \\
			& & A^{(a)}_{n,n,5} & 0 & A^{(a)}_{n,n,6} \\
		\end{pmatrix} \in \R^{(2n+1)\times(2n+3)}, \quad n = 0,1,2,\dots \\
	\tilde B^{(a)}_{x,n} &:= 
		\begin{pmatrix}
			0 & A^{(a)}_{n,0,4} & & \\
			A^{(a)}_{n,1,3} & \ddots & \ddots & \\
			& \ddots & \ddots & \tilde A^{(a)}_{n,n-1,4} \\
			& & A^{(a)}_{n,n,3} & 0
		\end{pmatrix} \in \R^{(2n+1)\times(2n+1)}  \quad n = 0,1,2,\dots \\
	\tilde C^{(a)}_{x,n} &:= 
		\begin{pmatrix}
			0 & A^{(a)}_{n,0,2} & & \\
			A^{(a)}_{n,1,1} & \ddots & \ddots & \\
			& \ddots & \ddots &A^{(a)}_{n,n-2,2} \\
			& & \ddots & 0 \\
			& & & A^{(a)}_{n,n,1} \\
		\end{pmatrix} \in \R^{(2n+1)\times(2n-1)}, \quad n = 1,2,\dots
\end{align*}
where $A^{(a)}_{n,k,j}$ are defined in equations (\ref{eqn:jacobisubblocksA1}, \ref{eqn:jacobisubblocksA2}, \ref{eqn:jacobisubblocksA3}). For $\tilde J_y^{(a)}$, the sub-blocks have sub-block-bandwidths $(3,3)$:
\begin{align*}
	\tilde A^{(a)}_{y,n} &:= 
		\begin{pmatrix}
			0 & B^{(a)}_{n,0,6} & 0 & & \\
			B^{(a)}_{n,1,5} & \ddots & \ddots & & \\
			& \ddots & \ddots & \ddots & \\
			& & B^{(a)}_{n,n,5} & 0 & B^{(a)}_{n,n,6} \\
		\end{pmatrix} \in \R^{(2n+1)\times(2n+3)}, \quad n = 0,1,2,\dots \\
	\tilde B^{(a)}_{y,n} &:= 
		\begin{pmatrix}
			0 & B^{(a)}_{n,0,4} & & \\
			B^{(a)}_{n,1,3} & \ddots & \ddots & \\
			& \ddots & \ddots & B^{(a)}_{n,n-1,4} \\
			& & B^{(a)}_{n,n,3} & 0
		\end{pmatrix} \in \R^{(2n+1)\times(2n+1)}  \quad n = 0,1,2,\dots \\
	\tilde C^{(a)}_{y,n} &:= 
		\begin{pmatrix}
			0 & B^{(a)}_{n,0,2} & & \\
			B^{(a)}_{n,1,1} & \ddots & \ddots & \\
			& \ddots & \ddots & B^{(a)}_{n,n-2,2} \\
			& & \ddots & 0 \\
			& & & B^{(a)}_{n,n,1} \\
		\end{pmatrix} \in \R^{(2n+1)\times(2n-1)}, \quad n = 1,2,\dots
\end{align*}
where $B^{(a)}_{n,k,j}$ are defined equations (\ref{eqn:jacobisubblocksB1}, \ref{eqn:jacobisubblocksB2}, \ref{eqn:jacobisubblocksB3}). For $\tilde J_z^{(a)}$, the sub-blocks are diagonal, i.e. have sub-block-bandwidths $(0,0)$:
\begin{align*}
	\tilde A^{(a)}_{z,n} &:= 
		\begin{pmatrix}
			\Gamma^{(a)}_{n,0,3} & 0 & \\
			0 & \ddots & \ddots & & \\
			& \ddots & \ddots & \ddots & \\
			& & 0 & \Gamma^{(a)}_{n,n,3} & 0 \\
		\end{pmatrix} \in \R^{(2n+1)\times(2n+3)}, \quad n = 0,1,2,\dots \\
	\tilde B^{(a)}_{z,n} &:= 
		\begin{pmatrix}
			\Gamma^{(a)}_{n,0,2} & \\
			& \ddots & & \\
			& & \ddots & \\
			& & & \Gamma^{(a)}_{n,n,2}
		\end{pmatrix} \in \R^{(2n+1)\times(2n+1)}  \quad n = 0,1,2,\dots \\
	\tilde C^{(a)}_{z,n} &:= 
		\begin{pmatrix}
			\Gamma^{(a)}_{n,0,1} & 0 & & \\
			0 & \ddots & \ddots & \\
			& \ddots & \ddots & 0 \\
			& & \ddots & \Gamma^{(a)}_{n,n-1,1} \\
			& & & 0 \\
		\end{pmatrix} \in \R^{(2n+1)\times(2n-1)}, \quad n = 1,2,\dots
\end{align*}
where $\Gamma^{(a)}_{n,k,j}$ are defined in equations (\ref{eqn:jacobisubblocksGamma1}, \ref{eqn:jacobisubblocksGamma2}).

@@
